### 2020-02-13 README.Rmd
Added CV grid

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
# library(blockCV)
```

@@

>>>>

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
```

@@

```{r, cache = TRUE}
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, k = 28, yOffset = 0.6
)

# Add foldID to data
bw_growth_df <- bw_growth_df %>% 
  mutate(
    foldID = bw_cv_grid$foldID,
    foldID = factor(foldID)
  )

# Visualize grid
bw_cv_grid$plots +
  geom_sf(data = bw_growth_df, aes(col=foldID), size = 0.1)
```

```{r, cache = TRUE}
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = 100, k = 28, yOffset = 0.6
)

# Add foldID to data
scbi_growth_df <- scbi_growth_df %>% 
  mutate(
    foldID = scbi_cv_grid$foldID,
    foldID = factor(foldID)
  )

# Visualize grid
scbi_cv_grid$plots +
  geom_sf(data = scbi_growth_df, aes(col=foldID), size = 0.1)
```
